prophet ir trumpas conclusionas

### 2023-05-22 Prophetas ir trumpas conclusionas.Rmd
.

---
title: "prophet ir trumpas conclusionas"
output: html_document
date: "2023-05-21"
---

@@

library(fable.prophet)

@@

>>>>

---
title: "prophet ir trumpas conclusionas"
output:
  pdf_document: Energy Trade Forecast
  html_document: default
date: "2023-05-21"
---

@@

```{r  Other forecasting models: Prophet, echo = FALSE}
library(fable.prophet)

@@

```
